Numerical Investigation of Stochastic and Determininstic Upscaling Methods for Permeability Fields; Using SVD

### 2018-03-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Started working on section title SVD application

\section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}

>>>>

\section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}\label{section:svd}
\section{A Brief Introduction to SVD}\label{subsection:svd_brief}

Singular Value Decomposition
